Detecting Facial Expressions in Professional Tennis Matches

### 2017-03-07 Report06-12.Rmd
report updates
kable table settings

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalcik"
date: "13 February 2017"
output: bookdown::pdf_document2
fig_caption: yes
fontsize: 11pt
documentclass: article
bibliography: references.bib
link_citations: yes
---

@@

```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
kable(SceneAttributes, format = "markdown", booktabs = TRUE, caption = "Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute.")
```

@@

```{r Solution-Specifications-Table, fig.cap = "\\label{tab:Solution-Specifications-Table}", results='asis',}
kable(SolutionSpecs, format = "markdown", booktabs = TRUE, caption="")
```

@@

```{r Face-Attribute-Tables, results='asis', fig.cap = "Attributes of an individual face within an image. The most appropriate option from the list was selected for each attribute.\\label{tab:Face-Attribute-Tables}"}
kable(FaceAttributes, format = "markdown", booktabs = TRUE)
```

@@

```{r Image-Characteristics-Table, fig.cap = "\\label{tab:Image-Characteristics-Table}"}
ImageCharacteristics <- ALLmetaIMG %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
ImageCharacteristics<-ImageCharacteristics[1:10,]
kable(ImageCharacteristics, booktabs = TRUE, caption="", format = "markdown")
```

@@

GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
kable(GoogleNoMatch[1:10,], caption="", format = "markdown")

@@

FaceCharacteristics<-arrange(FaceCharacteristics, desc(count))
FaceCharacteristics<-as.tbl(FaceCharacteristics[1:10,])
kable(FaceCharacteristics, caption="", format = "markdown")
```

@@

```{r Accuracy}
Accuracy<-with(ALLmetaIMG, table(ALLmetaIMG$matchesManual, ALLmetaIMG$type))
kable(Accuracy, caption="", format = "markdown")
# make this a proportional table, would this be necessary if we have the UpSetR
```

@@

kable(GoogleCharacteristics, format = "markdown", booktabs = TRUE, caption="")
```

>>>>

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalcik"
date: "13 February 2017"
output: bookdown::pdf_document2
fig_caption: yes
fontsize: 11pt
documentclass: article
bibliography: references.bib
biblio-style: apalike
link-citations: true
---

@@

```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
knitr::kable(SceneAttributes, format = "markdown", longtable=TRUE, booktabs = TRUE, caption = "Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute.")
```

@@

```{r Solution-Specifications-Table, fig.cap = "\\label{tab:Solution-Specifications-Table}", results='asis',}
knitr::kable(SolutionSpecs, format = "markdown", longtable=TRUE, booktabs = TRUE, caption="")
```

@@

```{r Face-Attribute-Tables, results='asis', fig.cap = "Attributes of an individual face within an image. The most appropriate option from the list was selected for each attribute.\\label{tab:Face-Attribute-Tables}"}
knitr::kable(FaceAttributes, format = "markdown", longtable=TRUE, booktabs = TRUE)
```

@@

```{r Image-Characteristics-Table, fig.cap = "\\label{tab:Image-Characteristics-Table}"}
ImageCharacteristics <- ALLmetaIMG %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
ImageCharacteristics<-ImageCharacteristics[1:10,]
knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, caption="", format = "markdown")
```

@@

GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
knitr::kable(GoogleNoMatch[1:10,], caption="", longtable=TRUE, format = "markdown")

@@

FaceCharacteristics<-arrange(FaceCharacteristics, desc(count))
FaceCharacteristics<-as.tbl(FaceCharacteristics[1:10,])
knitr::kable(FaceCharacteristics, caption="", longtable=TRUE, format = "markdown")
```

@@

```{r Accuracy}
Accuracy<-with(ALLmetaIMG, table(ALLmetaIMG$matchesManual, ALLmetaIMG$type))
knitr::kable(Accuracy, caption="", longtable=TRUE, format = "markdown")
# make this a proportional table, would this be necessary if we have the UpSetR
```

@@

knitr::kable(GoogleCharacteristics, format = "markdown", longtable=TRUE, booktabs = TRUE, caption="")
```
